Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Comment on concurrent connections
Use teletypefont for "meek"
Also, use xspace package for correct spacing after commands.

\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}

% Avoid line breaks in program names.
\def\meekclient{\mbox{meek-client}}
\def\meekserver{\mbox{meek-server}}
\def\meek{meek}
\def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}

@@

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek\ server's external interface is that of an ordinary web server.
Domain fronting enables a client to reach the server.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
We describe the results of an initial deployment.
\meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.

@@

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as pluggable transport~\cite{pt} for Tor.
\meek\ combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received from Tor
are returned to the client as HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{architecture}
\caption{
Architecture of \meek.
The client sends an HTTP request to the Tor bridge by way of an intermediate web service such as a CDN.
The client protects the bridge's domain name \textbf{forbidden.example} from the censor
by fronting it with another name, here \textbf{allowed.example}.
The intermediate web server decrypts the TLS layer and forwards the request to the bridge
according to the Host header.
The bridge sends data back to the client in the HTTP response.
\meekclient\ and \meekserver\ are transport plugins, the interface between Tor and \meek.
The host actually at allowed.example does not participate in the communication.
}
\label{fig:architecture}
\end{figure*}

\meek\ has been built into an alpha version of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other fronting-capable services
and deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek\ are now used by other circumvention systems
including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

% \meek\ is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
A quirk of the browser proxy model is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of
domain fronting with App Engine.
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek\ over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.

@@

% CORDON? Say how \meek\ would be classified in it?

@@

The components of the system are shown in Figure~\ref{fig:architecture}.
The parts that are new in meek
are the programs \meekclient\ and \meekserver,
which are the pluggable-transports~\cite{pt} interface with Tor.

\meekclient\ is essentially a web client that knows how to front HTTPS requests.
When \meekclient\ receives outgoing data from a client Tor process, it bundles them up into a POST request
and fronts the request through the web service,
which in turn forwards the request to \meekserver\ on the bridge.
If the response contains any HTTP body, \meekclient\ decodes it and returns it back to Tor.
\meekclient\ takes pains to make its TLS fingerprint
look like that of a browser; see Section~\ref{sec:browserextension}.

\meekserver\ is a special-purpose web server.
When \meekserver\ receives a request, it extracts the body and feeds it into
a local Tor process running as a bridge.
If there are any data pending to be sent back to the client from Tor,
\meekserver\ includes it in the body of the HTTP response.
\meekserver\ also handles session management:
because there may be many clients using the service at once,
the server must determine which client session each incoming request belongs to.
% It does this by means of an X-Session-Id header,
% described in this section.

When \meek\ is used with Google App Engine, one other component is needed:
a small ``reflector'' web app that simply copies any request
it receives and forwards it to a remote instance of \meekserver.
App Engine cannot directly run a Tor bridge,
so we bounce the requests to somewhere that can.
The reflector app emulates the behavior of an origin-pull CDN,
which also simply copies and forwards requests
when the response is not already cached.

The main technical challenge of the protocol is splitting up a TCP stream
into a sequence of HTTP requests and responses.
The underlying TCP stream is broken into chunks so that
it can be sent over HTTP.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order and without gaps and duplicates.
\meek\ takes a naive approach: requests and responses are strictly serialized.
The client doesn't send a second chunk of data
(i.e, make another HTTPS request) until it has
received the response to its first.
The reconstructed stream is simply the concatenation
of bodies in the order they arrive.
Doing it this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
Section~\ref{sec:discussion} proposes a more efficient encoding
that would enable multiple requests in parallel.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek\ HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-Id headers for classification.
}
\label{fig:protocol}
\end{figure}

\meekserver\ must handle many clients at once,
and therefore maintains many open connections to the local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for \meek, for two reasons:
the source IP of the requests is that of the intermediate web service,
not that of the client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Instead, each client generates a random 256-bit session ID for each new Tor stream,
which it sends with each of its requests in a special
X-Session-Id HTTP header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek\ uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send,
simply to give the server an opportunity to reply.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
The other technique,
implemented in Psiphon's version of \meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response stream it has open to the client and starts a new one.
This second technique is especially beneficial for bulk downloads,
but doesn't work on all services:
notably Google App Engine doesn't support streaming of this kind.

@@

\begin{center}
\begin{tabular}{r@{}r l}
          &    514 & Tor cell \\
          &  $+$29 & Tor TLS record \\
$\approx$ & $+$400 & meek HTTP header \\
$\approx$ &  $+$50 & meek TLS record \\
\hline
$\approx$ &   1000 & total
\end{tabular}
\end{center}

% >>> (1*543+450.)/(1*543)
% 1.828729281767956
% >>> (2*543+450.)/(2*543)
% 1.4143646408839778
% >>> (3*543+450.)/(3*543)
% 1.276243093922652
\noindent
The total overhead varies according to the length
of the Host field and the specifics of the intermediate web service's TLS,
but is somewhere in the neighborhood of $(543+450)/543-1\approx83$\%.
This is the worst case, when Tor sends a single cell.
Tor can bunch multiple cells into one transmission;
if two cells are sent at once, the overhead drops to
${\approx}41$\%; if three, it is ${\approx}28$\%.
Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
Persistent HTTP connections as used by Psiphon reduce overhead further,
because only one HTTP header is needed for a large number of transmissions.
Empty polling requests also use bandwidth,
but they are sent only when the connection is idle
so they don't affect upload or download speed.
As is discussed in Section~\ref{sec:trafficanalysis},
\meekclient\ reuses the same TLS connection for many requests,
so the fixed overhead of the initial TLS handshake is amortized.

@@

The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on the handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient\ is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
which are browsers, are different from Go's TLS; the browsers are also unlike each other.
A censor could block an uncamouflaged \meek\ using Go's fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

In order to disguise its TLS fingerprint,
\meekclient\ proxies all its HTTPS requests through an actual web browser.
We implemented extensions for two web browsers,
Firefox and Chrome,
that enable them to make HTTPS requests on behalf of \meekclient.
The TLS fingerprint looks like that of a browser, because it is that of a browser.
The browser instance running the extension is completely separate
from the browser the user interacts with.
It runs invisibly in the background in a separate process,
doesn't display a user interface,
and shares no state with the user's browser.

@@

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the client's computer.
The local Tor process starts a helper process that starts both \meekclient\
and the headless browser,
then configures \meekclient\ to proxy its requests through the browser extension.
The user's browser proxies through Tor;
Tor proxies through \meekclient,
and \meekclient\ proxies through the headless browser.
The headless browser is the only part that ever actually touches the network.
It should be emphasized that the URLs requested by the headless browser extension
have no relation to the URLs the user actually browses;
the extension only ever makes requests to the front domain.

The use of a browser extension brings benefits beyond TLS camouflage.
It means \meek's HTTP tunnel inherits other characteristics of the browser:
for instance
how often it resolves DNS names,
its connection reuse,
and its HTTP keepalive behavior.
The Firefox extension has special advantages
when \meek\ is used with Tor Browser
because Tor Browser
is a modified version of Firefox:
we can use the same browser executable for both the browser the user interacts with (Tor Browser)
and the one providing TLS camouflage (headless Firefox),
saving space in distribution packages
and sparing the user from having to separately configure a browser to run the extension.
In Tor Browser,
the headless Firefox is started and stopped transparently
when \meek\ is activated and deactivated.

@@

Appropriate TLS camouflage may differ depending on circumstances.
On a traditional desktop PC, using a browser is probably the right choice.
When Psiphon ported \meekclient\ to Android,
they didn't use a browser as camouflage,
but rather made all HTTPS requests with the standard Android HTTP API.
This decision makes sense because other Android applications
also use the standard API and share the same TLS fingerprint.

@@

CloudFlare~\cite{cloudflare},
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may simply block the domain entirely.
It is doubly bad when a domain is blocked, because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that doesn't send SNI.
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek\ does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

@@

One of our goals in developing \meek\ is to force
the censor to use relatively more expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek\ is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope that the censor will have to resort to measuring
more subtle features of the communication.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

% Advantage is that we are probably proxying web traffic.
As \meek\ is based on HTTPS,
we compare traffic traces of \meek\ against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek\ in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek\ trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from Lawrence Berkeley National Laboratory (LBL),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}

% Avoid line breaks in program names.
\newcommand{\meekclient}{\mbox{meek-client}\xspace}
\newcommand{\meekserver}{\mbox{meek-server}\xspace}
\newcommand{\meek}{\texttt{meek}\xspace}
\def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}

@@

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek server's external interface is that of an ordinary web server.
Domain fronting enables a client to reach the server.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
We describe the results of an initial deployment.
\meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.

@@

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as pluggable transport~\cite{pt} for Tor.
\meek combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received from Tor
are returned to the client as HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{architecture}
\caption{
Architecture of \meek.
The client sends an HTTP request to the Tor bridge by way of an intermediate web service such as a CDN.
The client protects the bridge's domain name \textbf{forbidden.example} from the censor
by fronting it with another name, here \textbf{allowed.example}.
The intermediate web server decrypts the TLS layer and forwards the request to the bridge
according to the Host header.
The bridge sends data back to the client in the HTTP response.
\meekclient and \meekserver are transport plugins, the interface between Tor and \meek.
The host actually at allowed.example does not participate in the communication.
}
\label{fig:architecture}
\end{figure*}

\meek has been built into an alpha version of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other fronting-capable services
and deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek are now used by other circumvention systems
including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

% \meek is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek uses just a few high-value front domains on hard-to-block network infrastructure.
A quirk of the browser proxy model is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of
domain fronting with App Engine.
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.

@@

% CORDON? Say how \meek would be classified in it?

@@

The components of the system are shown in Figure~\ref{fig:architecture}.
The parts that are new in \meek
are the programs \meekclient and \meekserver,
which are the pluggable-transports~\cite{pt} interface with Tor.

\meekclient is essentially a web client that knows how to front HTTPS requests.
When \meekclient receives outgoing data from a client Tor process, it bundles them up into a POST request
and fronts the request through the web service,
which in turn forwards the request to \meekserver on the bridge.
If the response contains any HTTP body, \meekclient decodes it and returns it back to Tor.
\meekclient takes pains to make its TLS fingerprint
look like that of a browser; see Section~\ref{sec:browserextension}.

\meekserver is a special-purpose web server.
When \meekserver receives a request, it extracts the body and feeds it into
a local Tor process running as a bridge.
If there are any data pending to be sent back to the client from Tor,
\meekserver includes it in the body of the HTTP response.
\meekserver also handles session management:
because there may be many clients using the service at once,
the server must determine which client session each incoming request belongs to.
% It does this by means of an X-Session-Id header,
% described in this section.

When \meek is used with Google App Engine, one other component is needed:
a small ``reflector'' web app that simply copies any request
it receives and forwards it to a remote instance of \meekserver.
App Engine cannot directly run a Tor bridge,
so we bounce the requests to somewhere that can.
The reflector app emulates the behavior of an origin-pull CDN,
which also simply copies and forwards requests
when the response is not already cached.

The main technical challenge of the protocol is splitting up a TCP stream
into a sequence of HTTP requests and responses.
The underlying TCP stream is broken into chunks so that
it can be sent over HTTP.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order and without gaps and duplicates.
\meek takes a naive approach: requests and responses are strictly serialized.
The client doesn't send a second chunk of data
(i.e, make another HTTPS request) until it has
received the response to its first.
The reconstructed stream is simply the concatenation
of bodies in the order they arrive.
Doing it this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
Section~\ref{sec:discussion} proposes a more efficient encoding
that would enable multiple requests in parallel.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-Id headers for classification.
}
\label{fig:protocol}
\end{figure}

\meekserver must handle many clients at once,
and therefore maintains many open connections to the local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for \meek, for two reasons:
the source IP of the requests is that of the intermediate web service,
not that of the client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Instead, each client generates a random 256-bit session ID for each new Tor stream,
which it sends with each of its requests in a special
X-Session-Id HTTP header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send,
simply to give the server an opportunity to reply.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
The other technique,
implemented in Psiphon's version of \meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response stream it has open to the client and starts a new one.
This second technique is especially beneficial for bulk downloads,
but doesn't work on all services:
notably Google App Engine doesn't support streaming of this kind.

@@

\begin{center}
\begin{tabular}{r@{}r l}
          &    514 & Tor cell \\
          &  $+$29 & Tor TLS record \\
$\approx$ & $+$400 & \meek HTTP header \\
$\approx$ &  $+$50 & \meek TLS record \\
\hline
$\approx$ &   1000 & total
\end{tabular}
\end{center}

% >>> (1*543+450.)/(1*543)
% 1.828729281767956
% >>> (2*543+450.)/(2*543)
% 1.4143646408839778
% >>> (3*543+450.)/(3*543)
% 1.276243093922652
\noindent
The total overhead varies according to the length
of the Host field and the specifics of the intermediate web service's TLS,
but is somewhere in the neighborhood of $(543+450)/543-1\approx83$\%.
This is the worst case, when Tor sends a single cell.
Tor can bunch multiple cells into one transmission;
if two cells are sent at once, the overhead drops to
${\approx}41$\%; if three, it is ${\approx}28$\%.
Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
Persistent HTTP connections as used by Psiphon reduce overhead further,
because only one HTTP header is needed for a large number of transmissions.
Empty polling requests also use bandwidth,
but they are sent only when the connection is idle
so they don't affect upload or download speed.
As is discussed in Section~\ref{sec:trafficanalysis},
\meekclient reuses the same TLS connection for many requests,
so the fixed overhead of the initial TLS handshake is amortized.

@@

The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on the handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
which are browsers, are different from Go's TLS; the browsers are also unlike each other.
A censor could block an uncamouflaged \meek using Go's fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

In order to disguise its TLS fingerprint,
\meekclient proxies all its HTTPS requests through an actual web browser.
We implemented extensions for two web browsers,
Firefox and Chrome,
that enable them to make HTTPS requests on behalf of \meekclient.
The TLS fingerprint looks like that of a browser, because it is that of a browser.
The browser instance running the extension is completely separate
from the browser the user interacts with.
It runs invisibly in the background in a separate process,
doesn't display a user interface,
and shares no state with the user's browser.

@@

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the client's computer.
The local Tor process starts a helper process that starts both \meekclient
and the headless browser,
then configures \meekclient to proxy its requests through the browser extension.
The user's browser proxies through Tor;
Tor proxies through \meekclient,
and \meekclient proxies through the headless browser.
The headless browser is the only part that ever actually touches the network.
It should be emphasized that the URLs requested by the headless browser extension
have no relation to the URLs the user actually browses;
the extension only ever makes requests to the front domain.

The use of a browser extension brings benefits beyond TLS camouflage.
It means \meek's HTTP tunnel inherits other characteristics of the browser:
for instance
how often it resolves DNS names,
its connection reuse,
and its HTTP keepalive behavior.
The Firefox extension has special advantages
when \meek is used with Tor Browser
because Tor Browser
is a modified version of Firefox:
we can use the same browser executable for both the browser the user interacts with (Tor Browser)
and the one providing TLS camouflage (headless Firefox),
saving space in distribution packages
and sparing the user from having to separately configure a browser to run the extension.
In Tor Browser,
the headless Firefox is started and stopped transparently
when \meek is activated and deactivated.

@@

Appropriate TLS camouflage may differ depending on circumstances.
On a traditional desktop PC, using a browser is probably the right choice.
When Psiphon ported \meekclient to Android,
they didn't use a browser as camouflage,
but rather made all HTTPS requests with the standard Android HTTP API.
This decision makes sense because other Android applications
also use the standard API and share the same TLS fingerprint.

@@

CloudFlare~\cite{cloudflare},
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may simply block the domain entirely.
It is doubly bad when a domain is blocked, because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that doesn't send SNI.
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

@@

One of our goals in developing \meek is to force
the censor to use relatively more expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope that the censor will have to resort to measuring
more subtle features of the communication.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

% Advantage is that we are probably proxying web traffic.
As \meek is based on HTTPS,
we compare traffic traces of \meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from Lawrence Berkeley National Laboratory (LBL),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.
